\documentclass{article}

\usepackage[english]{babel}
\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{setspace}
\usepackage{natbib}


\begin{document}

\title{Megatron Writeup}
\author{Ted Smith and Rahul Ram}
\date{October 21, 2013}

\maketitle

Megatron is a source-to-source rewriter that adds profiling
instrumentation to Javascript programs.  
Megatron is based around a general framework for Javascript
manipulation using a visitor pattern.

\section{Implementation}

Megatron contains three main components:

\begin{itemize}
\item visit.js, a framework for transforming Javascript ASTs
\item rewrite.js, a client of visit.js that converts javascript to
  profiled javascript
\item runtime.js, a small library embedded in the output of rewrite.js
  that contains various functions related to profiling.
\end{itemize}

Megatron's rewriter is implemented as four passes over the AST.

The first pass stores the names of all declared functions for later
use.

The second pass rewrites every function and function expression to
return an object with three fields: ``megatron\_func\_id'',
``megatron\_ret'', and ``megatron\_this''. The first is used to build a
call graph that resolves calls to the same function via different
identifiers as a result of dynamism. The second is the original return
value of the function. The third is the ``this'' construct, which is
returned in the event the function invocation occurred inside a
``new'' expression.

The third pass rewrites every function call to an invocation of the
Megatron runtime function ``log\_call''. ``log\_call'' is passed two
strings representing the caller and callee function, a thunk that will
return the value of the call, and a boolean that is true if
``log\_call'' is wrapping an invocation of ``new''. ``log\_call''
Functions invoked by ``new'' implicitly return the ``this'' object, so
Megatron must override its default behavior and return ``this'' rather
than the return value of the constructor function, which is usually
``undefined''. ``log\_call'' also takes the ``this'' object as a
parameter. Without explicitly passing ``this'', Megatron would
evaluate the thunk in the global ``this'' environment, causing
programs to execute incorrectly.

The final pass rewrites every reference to a function declared as per the table in the first pass. This is a conservative measure to ensure that function objects which leave the edges of the profiled application have the expected return value.

\section{Interface}

\subsection{Web Interface}

The web interface has the following paths 
\begin{itemize}
\item  "/" The index page allows user to enter the javascript code to be profiled.
\item  "/rewrite" The rewrite displays all result from instrumented code.
\item "/graph"  Generates Call Graph and Frequency of calls for all functions.
\end{itemize}


\subsection{Streaming of Objects}

Two channels (gobjects, graph)are created between client and server. 
The gobject channel allows receiver to stream the info regarded the profiled object 
back to server. In the graph channel the server streams the crunched profiled object back
to client which is later piped to input the graph.


\subsection{Graph Rendering}

We use springy.js library for renedering the  object values of graph.
The objects that are streamed from server are added to edges of the graph and then rendered.

\section{Results}

\begin{table}[t!]
\centering
\small
\newcommand{\siqr}[1]{\scriptsize(#1)}
\begin{tabular}{|r|r|r|}
\hline
\textbf{Program} & \textbf{Med.} (profiled) & \textbf{Med.} (standard) \\
\hline
fannkuch-redux & 82.0006430149 & 68.6592299938 \\
fasta & 20.8912289143 & 416.071839094 \\
k-nucleotide & 0.2661221027 & 4.9718329907 \\
n-body & 40.6880369186 & 857.941665888 \\
regex-dna & 0.027422905 & 0.0353209972 \\
reverse-complement & 0.0171220303 & 0.0375170708 \\
spectral-norm & 15.1626989841 & 0.0174901485 \\
\hline
\end{tabular}
\caption{Median of 3 runs of the Alioth benchmark suite}
\label{tab:alioth}
\end{table}


Megatron is able to profile the Alioth benchmark suite. Its instrumentations incur significant overhead, but since all function calls are uniformly slowed down, the profiling information it extracts should display the same relative relative times. Not included is the binary-tree benchmark, which takes roughly an hour to run on our test system and was impossible to obtain numbers for in a reasonable time. 



\end{document}


